\chapter{Objectives and Motivation}

The initial reason why I chose this project was to simplify how people find their location inside a building.\\
After losing my way multiple times in different buildings, such as airports, shopping malls, university campuses etc... I decided that there should be a better way. After a consistent research in the field I discovered that there were already solutions out there and they covered a few airports, a few shopping malls etc... Therefore I realised I had to come up with something original to add to the existing solutions and my main thought was focused on the price.\\
My research brought up the fact that the implementation of this technique can be really expensive, so I had to find a better way of doing it.\\
I came up with an idea, which had not been done before and could reduce the cost significantly.\\
I asked myself: instead of having hundreds of sensors, why not have only a few in critical spots and use other people's mobile phones as sensors themselves? e.g. Let's say there are 3 sensors in a specific area; while the user is in that area, they can easily find their location. What if the user walks out of range for one of the sensors? They will not be able to localise themselves anymore and would need more sensors. But what if instead of adding more sensors, the user "out of range" localise himself according to the position of 3 people's phones which are currently inside the range of the 3 initial sensors? This would create a chain where people localise themselves based on other people's location, which, in turn, are based on the initial fixed sensors.\\
This idea became my main goal.\\

\begin{center}
	REQUIREMENTS
\end{center}
The user must have their mobile phones turned on and the apposite app downloaded and opened. The screen must be on at all times, or the system will not work. \\
The goal is achieved only if the indoor place is equipped with appropriate sensors (beacons) and those were configured in the app before hand.

