\chapter{Introduction}
Since the invention of GPS, the mankind has relied on it for localisation and navigation purposes. Humans use it on a daily basis. They use it to get from point A to point B, to send their location to a friend, who can then join them for the evening out or they use when uploading a picture on Instagram, so their friends know where it was taken and so much more...\\
The only issue with GPS is that its functionalities are of no use indoors, because the signal cannot pass through walls. So how do we detect our position inside a building? A new technique has recently been introduced, which goes on with the name of Indoor Localisation.\\
It consists of calculating the location, of typically a smartphone user, indoors, where the GPS signal is absent.
The reason why human beings need to know their indoor position is the same as when they are outdoors. They want to know where they are, furthermore, they want to know how to get where they need to go.
The need of such technology is rapidly increasing in many sectors. The Retail industry has been recently affected. The reason behind, goes beyond the simple “from point A to point B”. The technology in this sector has enabled supermarkets to track the position of each user, which enables the centre to send deals and promotions of particular products to the costumers, depending on where they are located in the store. This has been proven to increase the retail’s sales.
Another field are the airports. The technology enables the user to easily find their terminals/gates without the worry of missing the flights because they spent to much time trying to understand where to go.
One more field is Healthcare. It enables to track high value equipment, monitor the location and temperature of medicines, save time searching for equipment and monitor vulnerable patients.\\
And the list goes on.
But how does the smartphone calculate somebody’s position indoors? Without the need of the GPS?
There are different methods to achieve the same results. The method used for this project involves the use of beacons.\\
The definition of a beacon is a bluetooth device which transmits specific packages, that can be read by an appropriate app and used to estimate the distance to it. They can be small sensors, which can fit in the palm of humans' hands, or also recent smartphones or tablets can be configured to send those packages.\\
Both these small devices and smartphones will be used throughout this project.\\
A detailed description will be provided in chapter 3 (Literature review).